Graph-Based Neural Reconstruction from Skeletonized 3D Networks

### 2018-03-12 papers/eccv2018/3_evaluation.tex
method description in 4.2 + overall comments

% !TEX root =  paper.tex
\section{Experimental Results}

We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from mouse and fly brains.

@@

The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the z-watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.

@@

\begin{table}[h!]
	\centering
	\begin{tabular}{l l} \hline
		\textbf{Parameters} & \textbf{Values} \\ \hline
		Loss Function & Mean Squared Error \\
		Optimizer & SGD  with Nesterov Momentum \\
		Momentum & 0.9 \\
		Initial Learning Rate & 0.0001 \\
		Decay Rate & $5 * 10^{-8}$ \\
		Activation & LeakyReLU $(\alpha = 0.001)$ \\
		Kernel Sizes & $3 \times 3 \times 3$ \\
		Filter Sizes & $16 \to 32 \to 64$ \\ \hline
	\end{tabular}
	\caption{Training parameters.}
	\label{table:architecture}
\end{table}

>>>>

% !TEX root =  paper.tex
\section{Experimental Results}
\TODO{right now, too many subsections. shall we break it into "Setup" and "Results"}
We evaluate our method by comparing it to a state-of-the-art pixel-based reconstruction approach using datasets from mouse and fly brains.

@@

%The segmentation of the Kasthuri dataset was computed by agglomerating 3D supervoxels produced by the watershed algorithm from 3D affinity predictions~\cite{zlateski2015image}. 
%A recent study by Funke et al.~\cite{funke2017deep} demonstrated superior performance of such methods over existing ones on anisotropic data. 
%We learn 3D affinities using MALIS loss with a U-net~\cite{ronneberger2015u,Turaga:2009}. 
%We apply the z-watershed algorithm with suitable parameters to compute a 3D oversegmentation of the volume. 
%The resulting 3D oversegmentation is then agglomerated using the technique of context-aware delayed agglomeration to generate the final segmentation~\cite{10.1371/journal.pone.0125825}.
For the Kasthuri dataset, we used the segmentation pipeline from Funke et al.~\cite{funke2017deep}. 
We first trained a 3D affinity prediction U-Net model~\cite{ronneberger2015u} with Malis loss~\cite{Turaga:2009} and applied the watershed and agglomeration method~\cite{funke2017deep} to obtain the final segmentation result.

@@

\TODO{we don't have space for the table for training parameters: move to supp}
\begin{table}[h!]
	\centering
	\begin{tabular}{l l} \hline
		\textbf{Parameters} & \textbf{Values} \\ \hline
		Loss Function & Mean Squared Error \\
		Optimizer & SGD  with Nesterov Momentum \\
		Momentum & 0.9 \\
		Initial Learning Rate & 0.0001 \\
		Decay Rate & $5 * 10^{-8}$ \\
		Activation & LeakyReLU $(\alpha = 0.001)$ \\
		Kernel Sizes & $3 \times 3 \times 3$ \\
		Filter Sizes & $16 \to 32 \to 64$ \\ \hline
	\end{tabular}
	\caption{Training parameters.}
	\label{table:architecture}
\end{table}
